\documentclass[a4paper,11pt]{scrartcl}
\usepackage[top=2cm,bottom=2cm,left=2.5cm,right=2.5cm]{geometry} % Seitenränder einstellen
\usepackage[english]{babel} % Worttrennung nach der neuen Rechtschreibung und deutsche Bezeichnungen
\usepackage[utf8]{inputenc} % Umlaute im Text
%\usepackage[scaled]{helvet} % Schriftart Helvetica
%\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc} % Trennung von Umlauten
\usepackage[dvipsnames]{xcolor} % Farbe in Dokument
\definecolor{tumblau}{rgb}{0,0.40234375,0.7734375} % eigene Farbe definieren
\parindent 0pt % kein Einrücken bei neuem Absatz
\usepackage{amsmath} % zusätzliche mathematische Umgebungen
\usepackage{amssymb} % zusätzliche mathematische Symbole
\usepackage{bbold} % zusätzliche mathematische Symbole
\usepackage{units} % schöne Einheiten und Brüche
\usepackage[square]{natbib} % wissenschaftliches Literaturverzeichnis
%\usepackage[printonlyused]{acronym} % Abkürzungsverzeichnis
\usepackage{icomma} % kein Leerzeichen bei 1,23 in Mathe-Umgebung
\usepackage{wrapfig} % von Schrift umflossene Bilder und Tabellen
\usepackage{picinpar} % Objekt in Fließtext platzieren (ähnlich zu wrapfig)
\usepackage{scrhack} % verbessert andere Pakete, bessere Interaktion mit KOMA-Skript
\usepackage{float} % bessere Anpassung von Fließobjekten
\usepackage{pgf} % Makro zur Erstellung von Graphiken
\usepackage{tikz} % Benutzeroberfläche für pgf
\usepackage[
margin=10pt,
font=small,
labelfont=bf,
labelsep=endash,
format=plain
]{caption} % Einstellungen für Tabellen und Bildunterschriften
\usepackage{subcaption} % Unterschriften für mehrere Bilder
\usepackage{enumitem} % no indentation at description environment
\usepackage[onehalfspacing]{setspace} % Änderung des Zeilenabstandes (hier: 1,5-fach)
\usepackage{booktabs} % Einstellungen für schönere Tabellen
\usepackage{graphicx} % Einfügen von Grafiken -> wird in master-file geladen
\usepackage{url} % URL's (z.B. in Literatur) schöner formatieren
\usepackage[pdftex]{hyperref} % Verweise innerhalb und nach außerhalb des PDF; hyperref immer als letztes Paket einbinden
\hypersetup{
pdftitle = {},
pdfauthor = {},
pdfsubject = {},
pdfproducer = {LaTeX},
pdfkeywords = {},
colorlinks,
linkcolor = black,
citecolor = black,
filecolor = black,
urlcolor = blue
} % Einstellungen Dokumenteigenschaften und Farbe der Verweise
%\usepackage{pythonhighlight} % python highlighting

% define bordermatrix with brackets
\makeatletter
\def\bbordermatrix#1{\begingroup \m@th
  \@tempdima 4.75\p@
  \setbox\z@\vbox{%
    \def\cr{\crcr\noalign{\kern2\p@\global\let\cr\endline}}%
    \ialign{$##$\hfil\kern2\p@\kern\@tempdima&\thinspace\hfil$##$\hfil
      &&\quad\hfil$##$\hfil\crcr
      \omit\strut\hfil\crcr\noalign{\kern-\baselineskip}%
      #1\crcr\omit\strut\cr}}%
  \setbox\tw@\vbox{\unvcopy\z@\global\setbox\@ne\lastbox}%
  \setbox\tw@\hbox{\unhbox\@ne\unskip\global\setbox\@ne\lastbox}%
  \setbox\tw@\hbox{$\kern\wd\@ne\kern-\@tempdima\left[\kern-\wd\@ne
    \global\setbox\@ne\vbox{\box\@ne\kern2\p@}%
    \vcenter{\kern-\ht\@ne\unvbox\z@\kern-\baselineskip}\,\right]$}%
  \null\;\vbox{\kern\ht\@ne\box\tw@}\endgroup}
\makeatother



\title{\vspace{-1cm}Artifical Intelligence}
\subtitle{Exercise 6: Project Proposal} \date{\today}

\begin{document}
\maketitle

\section*{Team}
Sebastian Bek, Marvin Klaus, Daniela Schacherer
\section*{Problem Definition}

Nowadays, we get constantly more used to having AI systems ease our every day lives. In particular in the context of electronic devices we use the available features for facilitated text-processing. This can be observed on mobile phone or search engines. \\
We propose the development of an autocompletion and prediction system. For that purpose, we will build a model suggesting possible word-ending given a prefix. In advance, it will predict the following word relative to the cursor position.

\section*{Dataset and Agent Environment}

By means of collection of training data (sets), we will try to design a text bot gathering multiple text sources in diverse text files. We will use several datasets originating from e.g.:\\
\url{https://nlp.stanford.edu/links/statnlp.html#Corpora}

\section*{Approach}

We are planning to adress this task using an approach, considering machine learning. In terms of machine learning, we will implement the approach with neural networks, which are trained using a selected set of training data. Since we don't consider ourselves experts in AI, we can't assess how well-suited our approach is for the given task. However, as we are interested in neural networks, we would like to try this method in order to gain a deeper insight into the topic.\\

\emph{Possible Challenges:}\\
A possible challenge arises from words, which are occurring much more frequently than others, e.g. "in\/ the\/ that", since these do not indicate any hint about possibly following words. We have to cope with this task by finding an appropriate solution\/ fix. Other than that, we will have to deal with spelling mistakes of the user. We could think of a SpellCheck routine, suggesting the correctly spelled word and additionally the predicted next word.


\section*{Evaluation and expected results}

A designated test user will manually run and validate a series of tests, which have been considered and stored elaborately for generating ground truth data (i.e. reference result test data). 

\section*{Hardware}

We do not think we will require any specific hardware system, yet our approach's (execution and evaluation) requirements will not be especially demanding.

\end{document}